Calls for Service During 2021 Compared to Pre-Pandemic Forecast - Call Origin

### 2021-06-07 output/forecast_origin_plots.Rmd

  forecasts %>% 
    filter(call_origin %in% types) %>% 
    # Occasionally the ARIMA model may produce forecast confidence intervals
    # that are less than zero, which will not show up on the plot because we
    # have set the y axis to start at zero (to make changes in vertical position
    # on the axis representative of changes in magnitude). To deal with this we
    # will manually set the lower CI of the forecasts to be zero if it is less
    # than zero in the original forecast.
    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, actual_calls)) +
    geom_point(aes(incident_week, actual_calls, fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y") +
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = "Calls for service during 2021 compared to pre-pandemic forecast",
      subtitle = str_wrap(
        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
        80
      ),
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = "weekly count of calls for service",
      fill = "actual calls significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

>>>>

  forecasts %>% 
    filter(call_origin %in% types) %>% 
    # Occasionally the ARIMA model may produce forecast confidence intervals
    # that are less than zero, which will not show up on the plot because we
    # have set the y axis to start at zero (to make changes in vertical position
    # on the axis representative of changes in magnitude). To deal with this we
    # will manually set the lower CI of the forecasts to be zero if it is less
    # than zero in the original forecast.
    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, actual_calls)) +
    geom_point(aes(incident_week, actual_calls, fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y", 
                 limits = as.Date(c("2020-01-06", "2020-12-21"))) +
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = "Calls for service during 2021 compared to pre-pandemic forecast",
      subtitle = str_wrap(
        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
        80
      ),
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = "weekly count of calls for service",
      fill = "actual calls significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))
